Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-12-11 vesicle_code/docs/permeableVes/main.tex
yny

The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}. In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows in or out of the membrane to neutralize the osmotic gradient. In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB}.

@@

Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{}, solvent ph \cite{}, and the hydration  energy of the membrane \cite{}. In this work we focus on the intrinsic water permeability and study the hydrodynamics of a semipermeable membrane. Specifically we focus on the water permeability due to jump in normal membrane traction.

>>>>

The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}. Without aquaporins or other membrane channels that promotes water permeability, the intrinsic water permeability is known to depend on the temperature \cite{}, solvent ph \cite{}, and the hydration  energy of the membrane \cite{}. In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while the intrinsic water permeability of a lipid bilayer membrane is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB}.

In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows against the osmotic gradient across the membrane to neutralize the osmolarity.   The resultant swelling/shrinking of cell is inevitably coupled to changes in membrane tension and cell shape \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL}.
In this work we focus on the intrinsic water permeability and study the subtle balance between hydrodynamics and elasticity of a semipermeable membrane under various flowing conditions and confinement. Specifically we focus on the effects of intrinsic water permeability in a vesicle under stress due to flows and/or confinement.

@@
